---
title: Limpieza
author: Grupo super Claudia
---

```{r libraries, include=FALSE}
library(tidyverse)
```

## Datos

```{r data}
source("limpiar.R")

data_1 <- lt_house(read.csv("train.csv"))[,-1]

data <- data_1[,c(1:20, 80)]

str(data)
summary(data)
```

## Filter bad columns

The following variables are not considered:

* `street`: This variable could cause a bias
* `alley`: This variable has mostly NA's
* `utilities`: All have the same value
* `landslope`: Same as `street`
* `condition1`: Same
* `condition2`: Same
* `bldgtype`: Same
* `lotshape`: Same
* `mszoning`: Same
* `landcontour`: Same
* `lotconfig`: Same
* `lotfrontage`: Not really that relevant
* `overallqual`: Included in overall cond

```{r desc}
bad_columns <- c("street", "alley", "utilities", "landslope", "condition1", "condition2", "bldgtype", "lotshape", "mszoning", "landcontour", "lotconfig", "lotfrontage", "overallqual")

bad_columns_idx <- which(colnames(data) %in% bad_columns)

data <- data[, -bad_columns_idx]
summary(data)
```

## Correlate

`lotarea`, `yearbuilt` and `yearremodadd` seem relevant, let's analyze them further.

```{r cor}
pairs(data)
```

## Visualize

Lot area.

```{r vis}
data <- data[-which(data$lotarea > 20000),]
ggplot(data) + geom_point(aes(x = lotarea, y = saleprice))
ggplot(data, aes(x = yearbuilt, y = saleprice)) + geom_point() + geom_smooth(method = "lm", se = FALSE, col = "blue")
ggplot(data) + geom_point(aes(x = yearremodadd, y = saleprice))
```

## Compare correlations

```{r cors}
cor(data$lotarea, data$saleprice)

