---
title: "Goodness of fit"
author: "Felipe Clement"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(xts)
library(AER)
```

# Goodness of fit

Data for this model is the percentage growth of stock Suramericana with respect to stocks from other companies.

```{r load_data}
load("RetornosDiarios.RData")

data <- retornos.diarios
str(data)
class(data)
sapply(data, class)
head(data)

summary(data)
```

## Visualize Data

```{r visualize_data}
plot.xts(data)
```

## Correlations between stocks

```{r correlations}
cor(data)
```

## Model

```{r model}
model <- lm(data = data, formula = GRUPOSURA ~ .)
summary(model)
```

## Test model

Since p value is too high, it means we can not reject the null hypothesis of `Ho: CONCONCRET = OCCIDENTE = 0`, therefore, both these variables have no effect in the percent change for GRUPOSURA stock.  

```{r test_model}
hypothesis_matrix <- matrix(
  c(
    "CONCONCRET = 0",
    "OCCIDENTE = 0"
  ),
  nrow = 2, ncol = 1
)

linearHypothesis(model, hypothesis.matrix = hypothesis_matrix)
```

### Test similar coefficients

```{r test_similar}
hypothesis_matrix <- matrix(
  c(
    "ECOPETROL = 0.12",
    "EXITO = 0.12"
  ),
  nrow = 2, ncol = 1
)

linearHypothesis(model, hypothesis.matrix = hypothesis_matrix)
```
