---
title: Multicollinearity
author: Felipe Clement
---

```{r libs}
library(car)
```

## Load data

```{r load}
data <- read.csv("data.csv")
str(data)
head(data)
```

### Create squared experience

```{r squared}
data$exp2 <- data$exp * data$exp
str(data)
head(data)
```

## Model

```{r model}
model <- lm(Lnih ~ yedu + exp + exp2 + sexo + sexo * yedu + sexo * exp + sexo * exp2, data)
summary(model)
```

## Coeffiecient VIFs

Tere is a collinearity problem with `exp, exp2, sex` and the latters combination with the others.

```{r vif}
vif(model)
```

## Kappa test

The result value is larger than 20, which indicates high collinearity.

```{r kappa}
X <- model.matrix(model)
XTX <- t(X) %*% X

eigenvalues <- eigen(XTX)$val

min_eigenvalue <- min(eigenvalues)
max_eigenvalue <- max(eigenvalues)

kappa <- sqrt(max_eigenvalue / min_eigenvalue)
kappa
```

## Conclusion

Since there is high collinearity, it could (in part) be due to `exp` and `exp2`, which, even if not directly linearly related, the range of observations could be small enough so that the cuadratic relation may be linearly approximated. We can't remove any of these variables, as there is a theoretical model behind them.
