---
title: Time series key concepts
---

```{r installs, include=FALSE}
library(httr)
library(dplyr)
library(xts)
```

This document will focus on key time series concepts, primarily statistical forecasting methods for forecasting.

A time series can interchangeably mean:

* An ordered set of variable observations
* A probabilistic model that describes the target variable behavior

## Types of forecasts

Two types of forecasts can be made with time series:

* **Qualitative**: Subjective predictions based on opinion, gut feeling, domain knowledge, experience, etc
  * Performed by an individual or group
  * No data is used

* **Quantitative**: Based on historical data

## Types of statistical methods

Statistical methods are divided into two categories:

* **Univariate**: Predict behavior of one variable based on its past behavior
* **Multivariate**: Predict behavior of one variable based on itself and others

## Components of a time series

A time series may be composed of:

* Trend
* Cyclical factor
* Seasonality
* Randomness

## Examples

Unemployment data from Colombia will be loaded from S3.

```{r load_unemployment_data}
employmentDataUrl <- "https://masters-datasets.s3.us-east-2.amazonaws.com/semester-2/analytics-fundamentals-2/timeseries/datosEmpleo.csv"

employmentDataRaw <- GET(employmentDataUrl)$content %>%
  rawToChar() %>%
  textConnection() %>%
  read.csv()

employmentDataRaw$mes <- as.Date(employmentDataRaw$mes, format = "%m/%d/%y")

head(employmentDataRaw)
```

A `ts` object will be formed from the data.

```{r tsify_unemployment_data}
employmentData <- ts(employmentDataRaw[, -1], start = c(2001, 1), frequency = 12)

head(employmentData)
periodicity(employmentData)
ts.plot(employmentData[, 1])
```

An `xts` object can also be formed.

```{r xtsify_unemployment_data}
employmentDataXts <- xts(employmentDataRaw[, -1], order.by = employmentDataRaw$mes)

plot.xts(employmentDataXts$TD_13ciudades)
```

Monthly monetary base for Colombia is loaded.

```{r load_monetary_base}
monetaryDataUrl <- "https://masters-datasets.s3.us-east-2.amazonaws.com/semester-2/analytics-fundamentals-2/timeseries/base.csv"

monetaryDataRaw <- GET(monetaryDataUrl)$content %>%
  rawToChar() %>%
  textConnection() %>%
  read.csv()

head(monetaryDataRaw)
```

A `ts` object is formed from this data.

```{r tsfy_monetary_data}
monetaryData <- ts(monetaryDataRaw, start = c(1980, 1), frequency = 12)

ts.plot(monetaryData)
```

Monetary base data can be decomposed multiplicatively since seasonal component seems to be directly proportional to the value of the series.

```{r decompose_base}
plot(decompose(monetaryData, type = "multiplicative"))
```

Unemployment data seasonality does not seem to depend on the value and can be decomposed additively.

```{r decompose_uneployment}
plot(decompose(employmentData[,1]))
```
