---
title: "Model Selection"
author: "Felipe Clement - Lina Quintero"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(formattable)
library(AER)
```

# Model Selection

## Load data
```{r load}
raw_data <- read.csv("data.csv")
str(raw_data)
head(raw_data)

data <- raw_data[, -1]
str(data)
head(data)
```

## Create models
```{r create_models}
model_1 <- lm(y ~ x1 + x2 + x3 + x6 + x7, data)
model_2 <- lm(y ~ x1 + x2 + x3, data)
model_3 <- lm(y ~ x4 + x5 + x8 + x9 + x10, data)

summary(model_1)
summary(model_2)
summary(model_3)
```

## Visualize Goodness of Fit

AIC and BIC suggest the best model is 2, while adjusted R squared suggests it's 1.

```{r visualize}
metrics_1 <- c(
  summary(model_1)$adj.r.squared,
  AIC(model_1),
  BIC(model_1)
)

metrics_2 <- c(
  summary(model_2)$adj.r.squared,
  AIC(model_2),
  BIC(model_2)
)

metrics_3 <- c(
  summary(model_3)$adj.r.squared,
  BIC(model_3),
  AIC(model_3)
)

customGreen0 <- "#DeF7E9"
customGreen <- "#71CA97"

row_names <- c("R Sq Adj", "AIC", "BIC")
consolidated <- data.frame(metrics_1, metrics_2, metrics_3, row.names = row_names)
formattable(consolidated,
  align = c("l", rep("c", 3))
)
```

## Compare Model 1 and 2

Since p-value is too high, we cannot reject the `H0: model_2`, therefore, model_1 is better.

```{r compare}
anova(model_2, model_1)
```

## Comparing Model 3

Since both p-values in each test mean we reject the respective null hypothesis of one model being better than the other, we can't conclude that either model is better than the other.

```{r compare_3}
jtest(model_1, model_3)
jtest(model_2, model_3)

coxtest(model_1, model_3)
coxtest(model_2, model_3)
```

## Conclusion

Since model 3 has worse Goodnes of Fit with respect to the others, and we can't prove it's better via J or Cox test, then we discard model 3. Regarding 1 and 2, the F test performed indicates model 
```{r conclusion}