---
title: Autocorrelation
author: Felipe Clement
---

```{r libs}
library(xts)
library(readxl)
library(tseries)
library(AER)
library(lmtest)
library(sandwich)
```

## Data

```{r data}
load("data.RData")

data_stocks <- retornos.diarios

str(data_stocks)
head(data_stocks)

data_dtf <- read_xlsx("data.xlsx")

str(data_dtf)
head(data_dtf)
```

### Join Data

Clean up DTF file data.

```{r clean}
colnames(data_dtf)[1] <- "fecha"

data_dtf$fecha <- as.Date(data_dtf$fecha)

data_dtf <- xts(data_dtf$DTF90dias, order.by = data_dtf$fecha)

str(data_dtf)
head(data_dtf)
```

Check periodicities match.

```{r match}
periodicity(data_stocks)
periodicity(data_dtf)
```

Join.

```{r join}
data <- merge(data_stocks, data_dtf, join = "left")

colnames(data) <- tolower(colnames(data))
colnames(data)[which(colnames(data) == "data_dtf")] <- "dtf"

str(data)
head(data)
```

## Model

```{r model}
model <- lm(gruposura ~ ., data)
summary(model)
```

## Residuals

First plot shows errors tend to switch sign "often", could be a sign of autocorrelation. Second plot shows there is not a strong correlation between the errors and their respective lagged errors.

```{r resid}
errors <- residuals(model)

par(mfrow = c(2, 1))

ts.plot(errors,
  main = "Estimated errors",
  xlab = "Days",
  ylab = "Errors"
)

lagged_errors <- lag.xts(errors)

plot(errors,
  lagged_errors,
  xlab = "errors in t",
  ylab = "errors in t-1",
  xlim = c(-6, 6),
  ylim = c(-6, 6)
)

lag_regression <- lm(errors ~ lagged_errors)

abline(lag_regression, col = "blue")
```

## Tests

All tests have `H0: no autocorrelation (random errors)`.

### Runs test

By the 3rd run of the test, we can reject the null hypothesis os no autocorrelation with 99.9% confidence and conclude that there is negative autocorrelation.

```{r tests}
error_signs <- factor(errors > 0)
head(error_signs)

runs.test(error_signs)
runs.test(error_signs, alternative = "less")
runs.test(error_signs, alternative = "greater")
```

### Durbin-Watson

Similar results to Runs test.

```{r dw}
dwtest(model, alternative = "two.sided")
dwtest(model, alternative = "greater")
dwtest(model, alternative = "less")
```

### Box-Pierce

```{r bp}
Box.test(errors)
```

### Breusch-Godfrey

```{r bg}
bgtest(model, order = 1)
```

## Solution

### New variance and covariance matrices

```{r newey_west}
covariances_newey <- NeweyWest(model)
covariances_andrews <- kernHAC(model)
covariances_lumley <- weave(model)
```

### New **t** values

All tests conclude that `conconcret`, `occidente` and `dtf` variables are individually insignificant.

```{r test}
coeftest(model, vcov. = covariances_newey)
coeftest(model, vcov. = covariances_andrews)
coeftest(model, vcov. = covariances_lumley)
```

### Test multiple coefficients

```{r test_coefficients}
model_restricted <- lm(gruposura ~ ecopetrol + nutresa + exito + isa + grupoaval + valorem, data)

waldtest(model_restricted, model, vcov = covariances_newey)
```
