---
title: R Samples
author: Felipe Clement
output: html_document
---

This file contains examples of basic R concepts and their variations.

## Vectors

This section refers to one dimensional vectors of elements (arrays in other languages).

### Declaration

Possible ways include:

```{r vectors_declaration}
c(1, 2, 3)

1:3

seq(-3, -1, 0.2)

rep(1, 5)
```

### Access

Vector access receives an _index vector_ to decide the output.

```{r example vector}
x <- c(0:6, NA)
x
```

#### Intger index vector access

The way it works when an _integer vector_ is passed is basically telling R to "give me the elements oredered by the following index list", this index list:

  - Does not have to be shorter than the original list
  - Can repeat indexes

```{r integer_vector_access}
# First element - R is 1-idexed (:
x[1]

# Same element more than once
x[c(3, 3, 3, 3)]

# Last  3 elements
x[length(x) - 3:0]

# All elements except the first two
x[-c(1:2)]
```

#### Logical index vector access

_logical vectors_ have the following conditions:

  - If longer than the original vector, will produce `NA` for every boolean value in the index vector in a position `y > length(x)`
  - If shorter than the original vector, will repeat the index vector until exactly all elements of the original have been evaluated

```{r logical_vector_access}
# Shorter than the original vector
x[c(TRUE, TRUE)]

# Shorter than the original but with a false
x[c(TRUE, FALSE)]

# Longer than the original
x[rep(TRUE, 10)]

# Elements not NA
x[!is.na(x)]

# Even elements
x[x %% 2 == 0]

# Even positive non NA elements
x[!is.na(x) & (x > 0) & (x %% 2 == 0)]
```
