---
title: Heteroscedasticity
author: Felipe Clement
---

```{r libs, include=FALSE}
library(lmtest)
```

## Data

```{r data}
data <- read.csv("data.csv")
str(data)
head(data)

data$exp2 <- data$exp * data$exp
str(data)
head(data)
```

## Model

```{r model}
model <- lm(Lnih ~ yedu + exp + exp2 + sexo + sexo * yedu + sexo * exp + sexo * exp2, data)
summary(model)
```

## Errors

```{r errors}
errors <- resid(model)
str(errors)
```

### Visualize

For `exp2` it is visuble that variance of the error decreases when `exp2` increases, this is a sign of heteroscedasticity.

```{r visualize_errors}
attach(data)
par(mfrow = c(2, 2))

plot(yedu, errors)
plot(exp, errors)
plot(exp2, errors)
plot(sexo, errors)

detach(data)
```

### Breusch-Pagan test

Since p-value is low, we can reject the `H0: homoscedasticity`, so there is heteroscedasticity cause by all variables. For `exp`, sinbce p-value is high, we can't reject the null hypothesis, therefore the variable does not uniquely cause heteroscedasticity.

```{r bp}
bptest(model, studentize = FALSE)
bptest(model, ~ data$exp,studentize = FALSE)
```
